\documentclass{article}
\usepackage[top=1.2in, bottom=1in, left=1in, right = 1in]{geometry}
%\usepackage[font=footnotesize,width = 0.8\textwidth]{caption}
\usepackage{titling}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{indentfirst}
\usepackage{lastpage}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{wrapfig}
\usepackage[inline]{enumitem}   % This allows me to enumerate things inline.
\usepackage{hyperref}

\hypersetup{
    pdftitle={CFA II Notes},
    pdfauthor={Runmin Zhang},
    %pdfsubject={Your subject here},
    %pdfkeywords={keyword1, keyword2},
    bookmarksnumbered=true,     
    bookmarksopen=true,         
    bookmarksopenlevel=1,       
    colorlinks=true,            
    pdfstartview=Fit,           
    pdfpagemode=UseOutlines,    % this is the option you were lookin for
    pdfpagelayout=TwoPageRight
}


\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\Ra}{$\Rightarrow$}
\setlength\parindent{0pt}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{CFA II Notes}
\fancyhead[R]{Runmin Zhang}
\fancyfoot[R]{\thepage}
\begin{document}
\tableofcontents
\newpage
\section{Reading 9: Correlation and Regressions}
\subsection{Sample covar and sample correlation coefficients}
Sample covariance: $cov_{x,y}=\sum_i \frac{(X_i-\bar X)(Y_i-\bar Y)}{n-1}$
\\Sample correlation coeff: 
$r_{x,y}=\frac{cov_{x,y}}{s_x s_y}$, where $s_x$ is the sample dev of X.
\subsection{Limtations to correlations analysis}
Outliers: The results will be affected by extreme data points.(outliers)\\
Spurious correlation: There might be some non-zero corrlation coeff, but 
acutally they have no correlation at all.\\
Nonlinear relationships: Correlation only describe the linear relastions.
\subsection{Hypothesis: determine if the population 
correlation coefficient is zero}
Two-tailed hypothesis test:
$$
H_0: \rho=0, H_a: \rho \neq 0
$$
Assume that the two populations are {\bf normally} distrubited, then we 
can use t-test:
$$
t=\frac{r\sqrt{n-2}}{1-r^2}
$$:
Reject $H_0$ if  $t>+t_{critical}$ or $t<-t_{critical}$. Here,$r$ is the
sample correlation. Remember, you need to check t-table to find the t-value.
\subsection{Determine dependent/indepedent variables in a linear regression}
{\bf Simple linear regression}: Explain the variation in a dependent variable 
in terms of the variabltion in a single indepedent variable.
{\bf Independent variables} are called explanatory variable, the exogenous 
variable, or the predicting variable. 
{\bf Dependent variable} is also called the explained variable, the endogenous 
variable, or the predicted variable.
\subsection{Assumptions in linear regression and interpret regression coeff.}
\begin{enumerate}
    \item Assumptions of linear regression:
        \begin{enumerate}
            \item Linear relationship must exist.
            \item The indepedent variable is uncorrelated with residuals.
            \item Expected Residual term is value. $E(\epsilon)=0$
            \item variance of the residual term is const. $E(\epsilon_i^2)=
                \sigma_\epsilon^2$. Otherwise, it will be "heteroskedastic"
            \item The residual term is independently distributed. otherwise -- "auto correlation"" 
                $E(\epsilon_i\epsilon_j)=1$    
            \item The residual term is normally distributed.
        \end{enumerate}
    \item Simple Linear Regression Model
        \begin{enumerate}
            \item Model: $Y_i=b_0+b_1X_i+\epsilon_i$, where $i=1...n$, and $Y_i$ is 
     the actual observed data.
            \item The fitted line, the line of best fit
                : $\hat{Y}=\hat{b_0}+\hat{b1}X_i$. Where $\hat{b_0}$
                is the estimated parameter of the model.
            \item How to choose the best fitted line? {\bf Sum of squared errors}
                 is minimum.
                 $$
                    \hat{b_1} = \frac{cov_{x,y}}{sigma_x^2}
                 $$
                 where $X$ is the indepdent variable. $\hat{b_1}$ is 
                 "regression coeffcient".
                 $$
                    \hat{b_0} = \bar Y - \hat{b_1}\bar X
                 $$
                 where $\bar X, \bar Y$ are the mean.
        \end{enumerate}
    \item Interpreting a regression coefficient: Similar to basic ideas of 
        "slope". Keep in mind: any conclusion regarding this parameter needs 
        the statistical significance of the slope coefficient.
\end{enumerate}
\subsection{Standard error of estimate, the coeff. of determination and a 
confidence interval for a regression coefficient.}
\begin{enumerate}
    \item Standard error of estimate (SEE): Standard deviation between $Y_{estimate}$
        and $Y_{actual}$. - Smaller: better
    \item Coefficient of Determination ($R^2$)
        The percentage of the total variance in the dependent variable that is 
        predictable from the indepedent variable. - One indepdent variable: $R^2=r^2$,
        where $r^2$ is the square of correlation coefficient.
    \item Regression Coefficient confidence interval
        \begin{enumerate}
            \item Hypothesis: $H_0: b_1=0 \Leftrightarrow H_a: b_1\neq 0$ 
            \item Confidence interval:
                $\hat{b_1}-(t_c s_{\hat{b_1}})<b_1<\hat{b_1}+(t_c s_{\hat{b_1}})$ 
            $s_{\hat{b}_1}$ is the standard error of the regression coeffi.  
        \end{enumerate}
\end{enumerate}
\subsection{Hypothesis: Determine if $\hat{b}_1=b_1$}
\begin{enumerate}
    \item t-test statistic: $t_{b_1}=\frac{\hat{b}_1 - b_1}{s_{\hat{b}_1}}$
    \item Reject: if $t>+t_{critical}$ or $t<-t_{critical}$
\end{enumerate}
\subsection{Calculate the predicted value for the depedent variable}
If an estimated regression model is known, $\hat{Y}=\hat{b}_0+\hat{b}_1 X_p$
\subsection{Calculate and interpret a confidence interval for the predicted 
value of the depedent variable}
\begin{enumerate}
    \item Eq: $\hat{Y}\pm(t_c s_f)$, where $s_f$ is the {\color{red}std error of the forecast.}
    \item $s_f^2=SEE^2 \left[1+\frac{1}{n}+\frac{(X-\bar X)^2}{(n-1)s_x^2} \right]$
        \begin{enumerate}
            \item $SEE^2=$ variance of the residuals
            \item $s_x^2=$ variance of the indepdent variable
            \item $X =$ value of the independent variable where the forecast was
                made.
        \end{enumerate}
\end{enumerate}
\subsection{ANOVA in regression. Interpret results, and calculate F-statistic}
\begin{enumerate}
    \item Analysis of variance (ANOVA) is used to analyze the total variability 
        of the depedent variable. 
        \begin{enumerate}
            \item Total sum of squares(SST): $SST=\sum_{i=1}^n(Y_i-\bar Y)^2$
                \\SST is the total variation in the depedent variable.
                $Variance=SST/(n-1)$
            \item Regression sum of squares(RSS): $RSS=\sum_{i=1}^n(\hat{Y}_i-\bar Y)^2$
                \\RSS is the explained variation.
            \item Sum of squared errors(SSE): $SSE=\sum_{i=1}^n(Y_i-\hat{Y}_i)^2$
                \\SSE is the unexplained variation.
            \item {\color{red}$SST = RSS+SSE$ I cannot get this equation yet}
                You need to know how to use these squares.
            \item Degree of freedom: i) Regression(Explained): $k=1$, since we only
                estimate one parameters.
                ii) Error(Unexplained) $df=n-k-1=n-2$
                iii) Total variation $df=n-1$
        \end{enumerate}
    \item Calculating $R^2$ and {\bf SEE}
        \begin{enumerate}
            \item $R^2=explained variation/total varn=RSS/SST$
            \item $\bf{SEE}=\sqrt\frac{SSE}{n-2}$ {\bf SEE} is the std deviation of the
                regression error terms.
        \end{enumerate}
    \item The F-Statistic: used to explain whether {\it at least one} indepdent parameter
        can significanly explain the dependent parameter.  
        \begin{enumerate}
            \item F-statistic eq: $F=\frac{MSR}{MSE}=\frac{RSS/k}{SSE/n-k-1}$
                 where $MSR=$ mean regression sum of squares.
                       $MSE=$ mean squared errors. 
                       Note: \color{red}{One tailed test!}
        \end{enumerate}
    \item F-statistic with one independent variable.
        \begin{enumerate}
            \item Hypothesis: $H_0: b1=0 \Leftrightarrow H_a: b1\ne 0$
            \item degree of freedom: $df_{rss}=k=1,df_{sse}=n-k-1$
            \item Decision rule: reject $H_0$ if $F>F_c$
        \end{enumerate}
\end{enumerate}
\subsection{Limitations of regression analysis}
    \begin{enumerate}
        \item Parameter instability: the estimation eq may not be useful for other times.
        \item Limited usefulness: other participants may also use the same eq.
        \item Assumptions does not hold: i) Heteroskedastic, i.e., non-const
            variance of the error terms. ii) autocorrelation, i.e., error terms
            are not independent.
    \end{enumerate}

\section{Reading 10: Multiple Regression and Issues in Regression Analysis}
Some basic ides
    \begin{enumerate}
        \item Model: 
            $Y_i=b_0+b_1 X_{1i}+b_2 X_{2i}+...+b_k X_{ki}+\epsilon_i$
        \item Multiple regression methodology estimates the intercept and 
            slope coefficients so that $\sum_i^n \epsilon_i^2$ is minimized.
    \end{enumerate}
\subsection{Interpret estimated regression coefficients and their p-values.}
They are just simple linear functions with multiple parameters. Ignore.
\subsection{Formulate a null/alternative hypothesis, do correspoding calculations}
\begin{enumerate}
    \item Hypothesis Testing of Regression coefficient. (Multi-parameters). \\
        Use t-statistics to determine if one parameter significantly contribute
        to the model.
        $$
            t=\frac{\hat{b}_j-b_j}{s_{\hat{b}_j}}, df=n-k-1
        $$
        where $k$ is the number of regression coefficients, and $1$ corresponds to
        the intercept term, and $s_{\hat{b}_j}$ is the coefficient standard error
        of $b_j$
    \item Determining statistical significance.
        \\ ``testing statistical significance" $\Rightarrow H_0: b_j=0, H_a: b_j\ne 0$
    \item Interpreting p-values.
        \begin{enumerate}
            \item Def: p-value is {\bf the smallest level of significance for 
                which the null hypothesis can be rejected.}
                \ If the p-value is less than significance level, the null 
        \end{enumerate}
    \item Other Tests of the Regression Coefficients: $H_0: a=$some value
\end{enumerate}
\subsection{Calculate and Interpret a confidence interval for the population 
value of a regression coefficient or a predicted value for the depedent variable
if an estimated regression model.}
\begin{enumerate}
    \item Confidence intervals for a regress. coeff.: $\hat{b}_j\pm(t_c\times s_{\hat{b}_j})$
    \item predicting the depedent variable: 
        $\hat{Y}_i=\hat{b}_0+\hat{b}_1 \hat{X}_{1i}+...+\hat{b}_k \hat{X}_{ki}$
        \\Even if you may conclude that some $b_i$ are not statistally significantly, you cannot
        treat them as $0$ and keep other parameters unchanged. You should use the
        original model, or you can throw $\hat{b}_k$ away and make a new regression model.
\end{enumerate}
\subsection{Assumptions of a multiple regresssion model}
\begin{enumerate}
    \item Linear relationships exist.
    \item The independent variables are not random, and there is no exact linear relation
        between indepdent variables.
    \item $E[\epsilon|X_1,...,X_k]=0$
    \item Variance of $\epsilon=0$, i.e. $E[\epsilon_i]=0$
    \item $E(\epsilon_i\epsilon_j)=0$
    \item $\epsilon$ is normally distributed.
\end{enumerate}
\subsection{Calculate and interpret F-statistic}
F-test: whether at least {\bf one} of the indepedent variables explains a significant
portion of the variation of the depedent variable. F test is a one-tail test.
\begin{enumerate}
    \item $H_0: b1=b2=b3=0 vs H_a:$ at least one $b_j\ne 0$
    \item $F=\frac{MSR}{MSE}=\frac{RSS/k}{SSE/n-k-1}$
    \item Degree of freedom: $df_{numerator}=k, df_{denominator}=n-k-1$
    \item Rules: reject $H_0$ if $F(test-statistic)>F_c(critical value)$
\end{enumerate}
\subsection{Distinguish between $R^2$ and adjusted $R^2$}
\begin{enumerate}
    \item coefficient of determination $R^2$: used to test if a group of indepedent
        variable can explain the depedent variable: 
        \\$R^2=\frac{total variation - unexplained variation}{total variation}
        =\frac{SST-SSE}{SST}=\frac{RSS}{SST}$
        \\{\bf Multiple R} = $\sqrt{R^2}$
    \item Adjusted $R^2$
        \begin{enumerate}
            \item Note: $R^2$: {\color{red}{Overestimating}}: will increase as variables are added to the model.
        Even the marginal contribution of new variables are not statistically significant.
            \item Introduce $R_a^2$: $R_a^2=1-\left[\left(\frac{n-1}{n-k-1}\right)\right](1-R^2)$
        \end{enumerate}
\end{enumerate}
\subsection{Evaluate the quality of a regression model by analyzing the ouput of the equation/ANOVA table}
\begin{enumerate}
    \item ANOVA Tables, some important quantities
        \begin{enumerate}
            \item $R^2=\frac{RSS}{SST}$
            \item $F=\frac{MSR}{MSE}$ with $k$ and $n-k-1$ df
            \item Standard error of estimate:$SEE=\sqrt{MSE}$
        \end{enumerate}
\end{enumerate}
\subsection{Formulate a multiple regression with dummpy variables to represent qualitative factors}
\begin{enumerate}
    \item Def: Some value is quite qualitative. Using dummy values like 0 or 1 
        to describe their impacts.
    \item Note: Pay attention to \# of dummy variables. If $n$ classes, we must use
        $n-1$ dummy variables.
    \item Interpreting the coefficients in a dummy variable regression. We can use F-statistics to
        test a group of parameters, or use t-test to test the individual slope coefficients.
    \item Example of Regression application with dummy variables. See Notes directly.
\end{enumerate}
\subsection{Why multiple regression isn't as easy as it looks?}
Pay attention to the assumptions that have been used. Violations like::
\begin{enumerate}
    \item Heteroskedasticity
    \item Serial correlation (auto-correlation)
    \item Multicollinarity
\end{enumerate}
Any violations on the assumptions will impact the estimation of SEE, and finaly 
change the t-statistic and F-statistic, and change the conclustion of the hypotesis
test.
\subsection{Types of Heteroskedasticity, how heteroskedasiticity and serial correlation affect inference}
\begin{enumerate}
    \item What is Heteroskedasticity?
        \\ {\bf Corresponding assumptions: Variance of the residuals is constant across observations. -- Homoskedasticity} 
        Heteroskedasity means the variance of the residuals is not equal.
        \begin{enumerate}
            \item Unconditional heter: Not related to the level of the indepedent
                variables. Will not systematiclly increase with changes in the value
                of the indepedent variables. {\color{red}Usually will not casue major problems.}
            \item Conditional heter: Related to the level of the independent variables. Eg:
                Conditional heter exists if the variance of the residuals increase with 
                the value of the independent variables increases. {\color{red}Will cause big problems.}
        \end{enumerate}
    \item Effect of Heteroskedasiticity on Regression Analysis
        \begin{enumerate}
            \item Unreliable standard errors.
            \item The coefficient estimates aren't affected.
            \item Will change the t-statistic, and will change the conclusion.
            \item Unreliable F-test
        \end{enumerate}
    \item Detect Heteroskedasicity
        \begin{enumerate}
            \item Scatter plot
            \item Breusch-pagan test: $BP test = n\times R^2_{resid}$ with $df=k$. 
                where $n=$the number of observations, $R^2_{resid}$=$R^2$ from a second
                regression of the squared residuals from the first regression. $k=$the number
                of independent variables. If $R^2$ or BP-test are too large, something is wrong.
        \end{enumerate}
    \item Correcting Heteroskedasticity
        \be
        \item Calculate robust sndard errors(White corrected std errors.). Use them for t-test.
            \item Generalized least squares. 
        \ee
    \item What is serial correlations?
        \be
            \item Def: auto-correlation, in which the residual terms are correlated.
                Common problem with time series data.
                \be
                    \item Positive serial correlation: a postive error in one time period will
                        increase the posibility to observe a positive one next time.
                    \item Negative serial correlation: Just opposite.
                \ee
            \item Effect: positive serial correlation will get small coefficient std errors. 
                Thus, too large t-statistics. therefore, too many Type I errors: reject the null
                hypothesis $H_0$ while it's actually true. 
            \item Detection:
                \be
                    \item Residual plots
                    \item Durbin-Watson statistics: 
                        $$
                        \color{red}DW=\frac{\sum_{t=2}^T (\hat{\varepsilon}_t-\hat{\epsilon}_{t-1})^2}{\sum_{t=1}^T \hat{\epsilon}^2}
                        $$
                        For large samples, $DW\approx 2(1-r)$, where $r$ is the 
                        correlation coefficient between residuals from one period and thoese from the previous period.
                        \\Results: 
                        \be
                            \item $DW=2\Rightarrow$ Homoskedasitic and not serially correlated.
                            \item $DW<2\Rightarrow$ Postively serially correlated.
                            \item $DW>2\Rightarrow$ Negatively serially correlated.

                        \ee
                        Formulated hypothesis with DW-table, upper and lower critical values
                        \be
                            \item Hypothesis: $H_0:$ the regression has {\bf no}
                                positive serial correlation.
                            \item $DW<d_l$: positive serially correlated. Reject null.
                            \item $d_l<DW<d_u$: inconclusive results.
                            \item $DW>d_u$: {\bf There is no evidence that are positive correlated.} 
                        \ee
                \ee
            \item Correcting serial correlation:
            \be
                \item Adjust the coefficient std errors. {\bf recommended.} Using Hansen method.
                    \be
                        \item Serial correlation only: Hansen method. 
                        \item Heteroskedasticity only: White-corrected stand errors.
                        \item Both: Hans methods.
                    \ee
                \item Imporoe the specification of the model.
            \ee
    \ee
\end{enumerate}
\subsection{Multicolinearity and its cause and effects in regression analysis}
Multicollinearity: Indepedent variables or linear combinations of independent variables are highly
correlated.
\begin{enumerate}
    \item Effect of Multicollinearity on Regression Analysis: Will increase the std errors of 
        the slope coefficients. {\color{red} Type II Error:
        A variable is significant, while we conclude it's not.} 
    \item Detecting: Common situation: $t-statistic$ is not significant while $F-test$ is significant.
        This tells us the indepedent variables are highly correlated.
        \\ A simple rule works if there are 2 indepedent variables: when the absolute value of the sample correlation betewen any two 
        indepedent variables in the regression is greater than 0.7.
    \item Correcting: omit one or more of the correlated indepedent variables. 
        THe problame is that it's hard to find the variables that result in the multicolinearity.
\end{enumerate}
\subsection{Model misspecification}
\begin{enumerate}
    \item Defination of {\bf Regression model of specification}: decide which independent variables
        to be included in the model.
    \item Types of misspecification
        \be
            \item The functional form can be misspecified:
                important variables are ommited;variables should be transformed; data is improperly pooled.
            \item Explanatory variables are correlated with error term in time series model:
                A lagged dependent variable is used as an independent variable; a function of the dependent
                variable is used as an independent variable(forecasting the past);
                independent variables are measured with error.
            \item Other time-series misspecification.
        \ee
\end{enumerate}
\subsection{Models with qualitive dependent variables}
Include qualitative dependent variables, like default, bankcrupcy. Cannot use an 
ordinary regression model. Should use other models like {\bf probit and logit models}
or {\bf discriminant models}.
\be
\item Probit: normal distribution, give probability.
\item Logistic: logistic distribution. 
\item Discriminant: result in an overall score or ranking.
\ee
% End Reading 10


%% Reading 11
\section{Reading 11: Time-Series Analysis}
\subsection{Calculate/evaluate the predicted trend value for a time series given 
the estimated trend coefficients}
\begin{enumerate}
    \item Linear Trend Model and Log-linear Trend
        \be
            \item Definition: $y_t=b_0+b_1(t)+\epsilon_t$ Note: $t$ is just time.
            \item Coefficients is determined by OLS. Ordinary least squared regression.
                \\$\hat{y}=\hat{b}_0+\hat{b}_1$
            \item Log-linear Trend Models
            \item Model: $y_t=\exp{b_0+b_1(t)}\Rightarrow \ln{y_t}=b_0+b_1(t)$
        \ee
\end{enumerate}
\subsection{Factors that determine whether a linear or a log-linear model trend 
should be used}
\be
    \item Factors that determine which model is best: plot data.
    \item Limitaions of trend models: 
        \be
            \item residuals are uncorrelated with each other.
        Otherwise, it will cause auto correlation and we should not use the trend model.
            \item For log-linear model, it is not suitable for cases with serial correlations (autocorrelation).
            \item Detect auto correlation: Durbin Watson statistic. $DW=2.0\Rightarrow$ No auto correlation.
        \ee
\ee
\subsection{Autoregressive model, requirements for covariance statinoary}
\be
    \item Autoregressive model:
        \be
            \item Model: $x_t=b_0+b_1 x_{t-1}+\varepsilon_t$
            \item Statistical inferences bse on ordinary least squares estimates doesn't
                apply unless the time series is {\bf covariance stationary}.
            \item Conditions for covariance stationary
                \be
                    \item Constant and finite expected value.
                    \item Constant and finite variance.
                    \item Constant and finite covariance between values at any given lag.
                \ee
        \ee
\ee
\subsection{An autogressive model of order $p$}
\be
    \item Model(order $p$): $x_t=b_0+b_1x_{t-1}+b_2x_{t_2}+...+b_px_{t-p}+\varepsilon_t$ 
    \item Forecasting with an autoregressive model: 
        \be
            \item One-period-ahead forecast for $AR(1)$: $\hat{x}_{t+1}=\hat{b}_0+\hat{b}_1 x_t$
            \item Two-period-ahead forecast for $AR(1)$: $\hat{x}_{t+2}=\hat{b}_0+\hat{b}_1 \hat{x}_{t+1}$
        \ee
\ee
\subsection{How the residuals can be used to test the autogressive model}
\be
    \item The residual should have no {\it serial correlation} if an AR model is correct.
    \item Steps
        \be
            \item Estimate: Start with AR(1)
            \item Calculate: the autocorrelations of he model residuals
            \item Test: whether the autoccorelations are signficantly different from 0.
                \\The standard error is $\frac{1}{\sqrt{T}}$ for $T$ observations. The t-test for each
                observation is $t=\frac{\rho_{\epsilon_t,epsilon_{t-k}}}{1/sqrt{T}}$, with $T-2$ df. 
        \ee
\ee
\subsection{Mean reversion and a mean-reverting level}
\be
    \item Mean reversion: The time series tends to move toward its mean.
    \item Mean-reverting level: $\hat{x}_{t+1}=x_{t}$, where $\hat{x}_t$ is the predicted value. 
    \item All covariance stationary time series has finite mean-reverting level. 
\ee
\subsection{Contrast in-sample and out-of-sample forecasts and the forecasting accuracy of 
different time-series models based on the root mean squared error criterion.}
\be
    \item in-sample, out-of-sample: determined by if the predicted data is in the range of 
        the observations.
    \item RMSE, root mean squared error: used to compare the accurancy. If the accurancy of 
        out-of-sample is better, you should use it for future applications
\ee
\subsection{Explain the instability of coefficients of time-series models}
\be
    \item Instability or nonstationarity. Due to the dynamic econimic conditions, 
        model coefficients will change a lot from period to period. 
    \item Shorter time series are more stable, but longer time series are more reliable.
\ee
\subsection{Random walk processes and their comparisons between covariance stationary processes}
\be
    \item Random walk: $x_t=x_{t-1}+\varepsilon_t$
    \be
        \item $E(\varepsilon_t)=0$: The expected value of each error is zero.
        \item $E(\varepsilon_t^2)=0$: The variance of the error terms is constant.
        \item $E(\varepsilon_i,\varepsilon_j)=0$: There is no serial correlation in the error terms.
    \ee
    \item Random walk with a Drift: $x_t=b_0+b_1 x_{t-1}+\varepsilon_t$, where $b_1$=0
    \item A random walk or a random walk with a drift have no finte mean-reverting level.
        Since $b_1=1,\frac{b_0}{1-b_1}=\frac{b_0}{0}$. Therefore, they are not covariance stationary.
    \item $b_1=1$, they exhibit a unit root. Thus, {\bf the least square regression that been used in 
        AR(1) will not work unless we transfrom the data}.
\ee
\subsection{Things about unit roots: when they will occur, how to test them, how to transform data to apply AR}
\be
    \item Unit root testing for nonstationarity:
        \be
            \item run an AR model and check autocorrelations
            \item perform Dickey Fuller test.
                \be
                    \item Transform: $x_t=b_0+b_1x_1+\varepsilon\Rightarrow x_t-x_{t-1}=b_0+(b_1-1)x_{t-1}+\varepsilon$
                    \item Direct test if $b_1-1=0$ using a modified t-test.    
                \ee
        \ee
    \item First differencing
        \be
            \item For a random walk, transform the data $y_t=x_t-x_{t-1}\Rightarrow y_t=\varepsilon_t$
                then start to use an AR model $y=b_0+b_1 y_{t-1}+\varepsilon$, 
                where $b_0=b_1=0$
            \item $y$ is covariance stationary.
        \ee
\ee
\subsection{How to test and correct for seasonality in a time-series model, and 
calculate and interpret a forecasted value using an AR model with a sesonal lag.}
\be
    \item Detect: special autocorrelation exists for some seasonal lags.
    \item Correction: Add an additional seasonal lag term.
\ee
\subsection{Explain autogressive conditional heteroskedasticity (ARCH) and describe
how ARCH models can be applied to predict the variance of a time series}
\be
    \item ARCH: the variance of the residuals in one period is dependent on the variance of
        the residuals in a previous period.
    \item Using ARCH models:
        \\Example $ARCH(1)$: $\hat{\varepsilon}_t^2=a_0+a_1\hat{\varepsilon}_{t-1}+\mu_t$
        if $a_1$ is significantly different from zero. $\hat{\varepsilon}_t^2$ is the squared residuals.
        \\Note: Things like generalized least squares should me used to 
                correct heteroskedasticity. otherwise, the std errors of the 
                coefficients will be wrong, leading to invalid conclusions.
    \item Predicting the variance of a time series: using ARCH model to predict the variance of 

        future periods: $\hat{\sigma}^2_{t+1}=\hat{a}_0+\hat{a}_1\hat{\varepsilon}_t^2$
\ee
\subsection{Explain How time-series variables should be analyzed for nonstationarity and/or cointegration before
use ain a linear regression}
\be
    \item Cointegration: 
        \be
            \item Two time series are economically linked or follow the 
        same trend and that relationship is not expected to change. -- Error terms 
        from regressing one on the other is covariance stationary and the t-test are reliable.
            \item How to test conintegration: regress $y_t$ on $x_t$ 
                 $y_t=b_0+b_1x_t+\varepsilon$, $y_t, x_t$ are two different time series.
                 Then do a unit root test using the Dickey Fuller test with critical t-values
                 calculated by Engle and Granger. 
                 \\If "A unit root" is rejected $\Rightarrow$ covariance stationary, cointegrated.
        \ee
\ee


\section{Reading 12: Probabilistic Approaches: Scenario Analysis, Decision Trees, and Simulations}
\subsection{Describe steps in a simulatino, Explain three ways to define the probability 
        distributions for a simulation's variable, and describe how to treat correlation accross
    variables in a simulation.}
        \be
            \item Steps in simulations:
                \be
                    \item Determine the probabilistic variables
                    \item Define probability distributions for these variables
                        \be
                            \item Option 1: Historical data
                            \item Option 2: Cross-sectional data: estimate the variable from similar 
                                companies.
                            \item Option 3: Pick a distribution and estimate the parameters.
                        \ee
                    \item Checkk for correlations among variables: Use historical data to deterine
                        whether any ststematically related. Strong relations$\Rightarrow$ 1) Allow only
                        one of the variables can be removed. Or 2) Build the rules of correlations
                        into the simulation.
                    \item Run the simulation.
                \ee

        \ee
\subsection{Describe advantages of using simulations in decision making}
\be
    \item Advantages: 1) Better input quality   2) Provides a distribution of expected value
        rather than a point estimate.
\ee
\subsection{Describe some common constraints introduced into simulations}
\be
    \item Constraints: specific limits imposed by users of simulations.
    \item Types of constraints
        \be
            \item Book value constraints:
                \be
                    \item Regulatory capital requirements: minimum capital requirements
                    \item Negative equity
                \ee
            \item Earnings and cash flow constraints: might be imposed to meet analyst expectations
            \item Market value constraints
        \ee
\ee
\subsection{Describe issues in using simulations in risk assessment}
\be
    \item Limitations of using simulations
        \be
            \item Input quality: garbage in, garbage out
            \item Inappropriate statistical distributions
            \item Non-statinoary distributions: parameters will change
            \item Dynamic correlations: correlations between input variables will change.
        \ee
    \item Risk-adjusted value: cash flows from simulations are not risk-adjusted. 
        SHOULD NOT be discounted at risk-free rate.
\ee
\subsection{Compare scenario analysis, decision trees, and simulations}
\be
    \item Scenario analysis: computes the value of an investment under some specific cases.
        Total probability is less than 1.
    \item Decision trees: good when risk is discrete and sequential. Sum of probability is 1
\ee

\section{Reading 13: Currency Exchange Rates: Determination and Forecasting}
\subsection{Calculate and interpret the bid-ask spread}
\be
    \item Exchange rates
        \be
            \item Important things: exchange rate, spot exchange rate, forward exchange rate.
            \item Bid/offer(ask) rates:
                //Bid: The price that bank will buy. Offer: The price that bank will sell.
            \item Foregin Exchange Spread. Unit: "1 pip"$=1/10000=0.0001$. Spread depend on:
                \be
                    \item Spread in the interbank market. (Currencies, time, market volatility)
                    \item Size of transaction.
                    \item Relationship between the dealer and client.
                \ee
        \ee
\ee
\subsection{Identify a triangular arbitrage opportunity and calculate its profit}
\be
    \item Example: USD/AUD. USD is the price currency, and AUD is the base currency.
        \be
            \item Buy the base currency at the ask $\Rightarrow$ Sell the price currency at the ask
            \item Sell the base currency at the bid $\Rightarrow$ Buy the price currency at the bid
        \ee
    \item For investors,Rule: {\it up-the-bid-and-multiply, down-the-ask-and-divide}
        \be
            \item Convert USD into AUD: going down the quote -- from USD on top 
                to AUD on bottom. Use the ask price for the quote.
            \item Convert AUD into USD: similar. But from bottom to top.
        \ee
    \item Cross Rate: The exchange rate between two currencies with the help by 
        a common third currency.
    \item Cross Rate with bid-ask spreads.
        \be
            \item Rule 1:
            $$
            \left(\frac{A}{C}\right)_{bid}=\left(\frac{A}{B}\right)_{bid}
            \times \left(\frac{B}{C}\right)_{bid};
            \left(\frac{A}{C}\right)_{offer}=\left(\frac{A}{B}\right)_{offer}
            \times \left(\frac{B}{C}\right)_{offer}
            $$
            \item Rule 2:
            $$
            \left(\frac{B}{C}\right)_{bid}=\frac{1}{\left(\frac{C}{B}\right)_{offer}};
            \left(\frac{B}{C}\right)_{offer}=\frac{1}{\left(\frac{C}{B}\right)_{bid}}
            $$
        \ee
    \item Triangular Arbitrage: If the dealer's quote is different from the cross
        rate, arbitrage opportunities may exist. Check it with Notes.
\ee
\subsection{Distinguish between spot and forward rates and calculate the forward
premium/discont for a given currency}
\be
    \item Forward premium relative to a second currency: 
        Forward price > Spot price. Forward premium = $F-S_0$
    \item Calculate the market-to-market value of a forward contract
            $$
                V_T=(FP_T-FP)(contract size)
            $$
            where:
            \be
                \item $V_T$ = value of the forward contract at time $T$, denominated
                    in price currency
                \item $T$ = maturity of the forward contract
                \item $FP$ = forward price locked in at inception to buy base currency
                \item $FP_T$ = forward price to {\bf sell} the same currency at time $T$
            \ee
    \item Value prior to expiration.
    $$
    V_t=\frac{(FP_t-FP)contract size}{1+R(\frac{days}{360})}
    $$
    where 
    \be
        \item $V_t$ is the value of the forward price
        \item $FP_t$: forward price at time $t$
        \item $days$ number of days remaining
        \item $R$ interest rate
    \ee
\ee
\subsection{Explaining international parity relations (covered and uncovered 
interest rate parity, purchasing power parity, and the international Fisher effect)}
\be
    \item Covered interest rate parity: ``Covered" means bound by arbitrage. 
        Investor should earn the same return using either currency.
        $$
            F=\frac{1+R_A(\frac{days}{360})}{1+R_B(\frac{days}{360})}S_0
        $$
    \item Uncovered interest rate parity: Forward currency contract is unavailable, 
        which makes the interest rate not bound by arbitrage.
        For a quote A/B, the base currency is expected to apprecitate
        $$
            E(\%\Delta_S)_(A/B)=R_A-R_B
        $$
        Uncovered interest rate parity can only {\bf forcast} the future spot exchange rate.
    \item Comparing covered and uncovered interest parity:
        \be
            \item Covered interest parity $\Leftrightarrow$ No-arbitrage forward rate
            \item Uncovered interest parity $\Rightarrow$ {\bf Expected} future spot rate
        \ee
    \item International Fisher Relation
        \be
            \item $R_{nominal}=R_{real}+E(inflation)$
            \item Under real interest rate parity, the real interest rate are 
                assumed to converge across different markets.
                $$
                    R_{nominal A}-R{nominal B}=E(inflation_A)-E(inflaction_B)
                $$
        \ee
    \item Purchasing Power Parity: Assumed by one price law.
        \be
            \item Absolute purchasing power parity: The average price of a basket
                of consumption goods.
                $$
                    S(A/B)=CPI(A)/CPI(B)
                $$
                May not hold due to different weights of consumptions.
            \item Relative Purchasing Power Parity: Changes in exchange rates 
                should exactly offset the price effects of any inflation differencital b
                between the two contries.
                $$
                \%\Delta S(A/B)=Inflation_A-Inflation_B=change in spot price(A/B)
                $$
                Not always held in short run.
            \item Ex-Ante Version of Purchasing Power Parity: Similar to relative PPP,
                but Ex-Ante uses expected inflation instead of actuall inflation.
        \ee
\ee
\subsection{Describe the relations among the international parity conditions}
See Notes Page 263, Vol. 2.
\subsection{Evaluate the use of the current spot rate, the forward rate, purchasing
parity and uncovered interest parity to forecast future spot exchange rates}
\be
    \item Real Exchange Rate = $S_t\left[\frac{CPI_B}{CPI_A} \right]$, $S_t$ is 
        the spot rate at time $t$ given as A/B
\ee
\subsection{Explain how flows in the balance of payment accounts affect currency
exchange rates}
\be
    \item Balance of Payments: accounting method to track transactions between a
        country and its international trading partners.
        \be
            \item Incluing government, consumer, and business transactions.
            \item current account + financial account + offcial reserve account = 0
            \item
                \be
                    \item Current account: Exchanges of goods/services, exchanges of
                        investment income and unilateral transfers like gifts.
                        \be
                            \item Surplus: we sell more to other countries, buy less from them
                            \item Deficit: we buy more from the rest, sell less to them
                        \ee
                    \item Financial account/Capital account: Flows of funds for debt
                        and equity investment into/out of a country. Surplus: Money is
                        flowing into the country.
                    \item Offcial resreve: thoes made from the reserves held by the government.
                        Normally doesn't change from year to year.
                \ee
        \ee
    \item Influence of BOP on Exchange Rates
        \be
            \item Current Account
                \be
                    \item Flow mechanism
                        \be
                            \item Deficit: increase the supply of that currency in the market. 
                                Because exporters to our countries need to convert
                                their revenue to their own currency. $\Rightarrow$ Down on the exchange
                                value.
                            \item Depreciation of the currency may rebalance the 
                                current account. Depending on {\bf The initial deficit, the influence
                                of exchange rates on import/export prices, price elasiticity of traded goods.}
                                See Notes P265 for details.
                        \ee
                    \item Portfolio Composion mechanism. Countries with current account surpluses
                        usually have capital account deficits, which typically take the form of investments
                        in countries with current account deficits. As a result of these flows of capital, investor
                        countries may find their portfolios' composition being dominated by few investee currencies. 
                        When investor countries decide to rebalance their investment portfolios, it can have a significant negative
                        impact on the value of those investee country currencies.
                    \item Debt sustainability mechanism: Current account deficit may be balanced
                        by borrowing money from other countries. If the debt too high, lenders may question
                        the security, leading to the deprecitaion of the borrower's currency.
                \ee
            \item Capital Account Influences: Money flow in$\Rightarrow$Demand for 
                my country's currency increases$\Rightarrow$Appreciation. 
                \be
                    \item Good: can help to overcome a shortage of internal savings
                    \item Bad: Too much money can be problematic for emerging markets.
                        \be
                            \item Excessive appreciation of the domestic currency
                            \item Financial asset, real estate bubbles
                            \item Increase in external debt
                            \item Excessive consumption in the domestic market funded by credit
                        \ee
                \ee

        \ee
    \item real exchange rate (A/B) = equilibrium real exchange rate (A/B) + (real interest rate$_B$ - real interest rate$_A$)
        -(risk premium$_B$ - risk premium$_A$) \\
        This eqution is not precise. We cannot use it to calculate the rate.
    \item Taylor Rule
        $$
            R=r_n+\pi+\alpha(\pi-\pi^\ast)+\beta(y-y^\ast)
        $$
        \be
            \item R = Central bank policy rate implied by the Taylor Rule
            \item $r_n$ = Neutral {\bf real} policy interest rate
            \item $\pi$ = Current inflation rate
            \item $\pi^\ast$ = Central bank's target inflation rate
            \item $y$ = log of current level of output
            \item $y^\ast$ = log of central bank's target (sustainable) output
            \item $\alpha, \beta$ = policy response coefficients. (suggested value: 0.5 for both)
        \ee
        $$
        Real interest rate = r = R-\pi=r_n+\alpha(\pi-\pi^\ast)+\beta(y-y^\ast)
        $$
        Substitute the real interest rate equation, we have\\
        Real exchange rate (A/B) = equilibrium real exchange rate(A/B) + differenc
        in neutral real policy interest rate(B-A)+$\alpha$[difference in inflation gap (B-A)]+
        $\beta$[difference in output gap(B-A)]-(risk premium$_B$-risk premium$_A$)
        //Where: Inflation gap = current inflation - target inflation, 
        Output gap = current output - target output
\ee
\subsection{Explain approaches to assessing the long-run fair value of an exchange rate}
\be
    \item The ex-ante version of relative PPP holds $\Rightarrow$ The real exchange rates constant. 
        However, relative PPP does not necessarily hold over the short term. Over long
        term, PPP holds, and the real rate will be near its equilibrium level.
    \item IMF asseses long-term equilibrium real exchanges rate based on
        \be
            \item Macroeconomic balance approach: if the Ex rates need to be adjusted to 
                equalize the expected current account imbalance and the sustainable current
                account imbalance.
            \item External sustainability approach. How rates need to be adjust to force
                a country's external debt relative to GDP towards its sustainable level.
            \item Reduced-form econometric model approach. 
        \ee
\ee
\subsection{Describe the carry trade and its relation to uncovered interest rate
parity and calculate the profit from a carry trade.}
\be
    \item FX carry trade: Invest in a higher yielding funding with the funds borrowed in
        a lower yielding currency. This is due to the uncovered interest rate parity may not
        hold.
    \item Risk of the Carry Trade
        \be
            \item The exchange rate may change abruptly.
            \item The return distribution is not normal. Negative skewness and 
                excess kurtosis (fat tails). $\Rightarrow$ High probabilithy of large loss
        \ee
    \item Risk Management in Carry Trades
        \be
            \item Volatility filter: if volatitlity > certain threshold, close the carry trade.
            \item Valuation filter: valuation band for each currency based on PPP. If the value
                of a currency falls below the band, we will increase its ratio.
        \ee
\ee
\subsection{Describe the Mundell-Fleming model, the monetary approach and the asset
market approach to exchange rate determination.}
\subsection{Forecast the direction of the expected change in an exchange rate based on
balance of payment, Mundell-Fleming, monetary, and asset market approaches to exchange rate determination.}
\subsection{Explain the potential effects of monetary and fiscal policy on exchange rates.}
\be
    \item Mundell-Fleming Model: evaluate the impact of monetary and fiscal policies on interest rates, 
        and therefore on exchange rates.
    \item Flexible Exchange Rate Regimes: rate are determined by markets.
        \be
            \item High Capital Mobility: Expansionalry M and F are likely to have
                opposite effects. Expansionary M will reduce the interest rate, 
                reduce the inflow of  capital investment, reduce the demand for 
                domestic money, depprecation.
            \item Low Capital Mobility: Uncertain
            \item Summary:\\
                \begin{tabular}{c c c}
                \hline
                Monetary/Fiscal & High Capital Mobility & Low Capital Mobility \\
                \hline
                Expan/Expan &   Uncertain   & Depreciation \\
                Expan/Restr &   Depreciation & Uncertain    \\
                Restr/Expan &   Appre       & Uncertain     \\
                Restr/Restr &   Uncertain   & Appreciation  \\
                \hline
                \end{tabular}   
            \item Fixed Ex rate regimes
                \be
                    \item If monetary expansionary (depreciation), governments need to buy money in the 
                        FX market, therefore will reverse the effect from monetary expansionary.
                    \item Fiscal expansionary \ra Appreciation(More money needed) \ra Government need to 
                        sell money to keep Ex rate stable. \ra Fiscal effect on aggregate demand will be reinforced.
                \ee
        \ee
    \item Monetary Approach to Exchange Rate determination\\
        Inflation play no role in exchange rate in Mundell-Fleming model.
        \\Assumptions: 1. Output is fixed.
        \be
            \item Method 1: Pure Monetary model. Assume: PPP holds, output is constant.
            \item Dornbusch overshooting model. Price are inflexible in short term.
                Expan Monetary \ra price increase, interest rate down \ra depreciatoin of currency.
                Therefore, in short term, price sticky, interest rate down too much. \ra depreciation is greater
                than PPP implies.
        \ee
    \item Portfolio Balance Approach to Exchange rate determination.
        \be
            \item It focues on long-term implications of fiscal policy on currency values.
            \item Fisical deficit\ra sell bonds\ra When investors thinks the country is safe, they will continue to buy bonds. 
                If the investors refuse to fund the deficits \ra depreciation
        \ee
    \item In short term, with free capital flows, expan fiscal \ra appreciation\\
        Long term\ra government has to reverse expan fiscal. Otherwise, investor
        will refuse to fund it, then the country have to monetize its debt (print money).\ra depreation

\ee
\subsection{Objectives of central bank intervention and capital controls and describe
the effectiveness of intervention and capital controls.}
See Notes P274. Old version.
\subsection{Describe warning signs of currency crisis.}
\be
    \item Terms of trade deteriorate
    \item Foreign reserve down quickly
    \item Real exchange rate is extremly higher than mean-reverting value.
    \item INflation increases.
    \item Equity markets have a boom-bust cycle.
    \item Money supply relative to bank reserves increases.
    \item Nominal private credit grows.
\ee
\subsection{Technical analysis}
See Notes P275 Old version.


\section{Economic Growth and the Investment Decision}
\subsection{Compare factors favoring and limiting economic growth in developed and developing economies}
Two important factors. 1: GDP per capita. 2: Growth of GDP
\be
    \item Preconditions for Growth
        \be
            \item Saving and investment. Positively correlated with economic development.
            \item Financial markets and intermediaries. Help resources reallocation. 
                However, it may increase leverage, risks.
            \item Political stability, rule of law and property rights.
            \item Investment in human capital. Worker's skills.
            \item Tax and regulatory systems. Lower tax burdens are good.
                Lower regulation levels are good.
            \item Free trade and unrestriced capital flows.
        \ee
\ee
\subsection{Describe the relation between the long-run rate of stock market appreciation and
the sustainable groth rate of economy.}
The growth in the price is related to earnings and GDP: 
$\Delta_P=\Delta_GDP + \Delta(E/GDP)+\Delta(P/E)$.
Over the long-term, $\Delta(E/GDP)=0,\Delta(P/E)=0$. Only GDP growth matters.
\subsection{Explain why potential GDP and its growth rate matter for equity and fixed income investors.}
Higer GDP growth\ra Higher interest rates \ra Higer real asset returns.\\
Higher GDP growth makes people think that future income is increasing, therefore increase consumptions
and reduce savings. To encourage consumers save, higher interest rate is needed.

In short term, actual GDP in excess of potential GDP will result in rising prices \ra inflationary pressure.
\subsection{Distinguish between capital deepening investment and technological progress and explain
how each affects economic growth and labor productivity}
\be
    \item Factor input and Economic growth
        \be
            \item Model: 2-factor aggregate production: Y~F(L,K) at a level of tech T.
                Output Y is a function of labor(L) and capital.
            \item Cobb-Douglas Production: $Y=TK^\alpha L^{(1-\alpha)}$
                \\Dividing both sides by $L$, the output per worker is 
                $$
                    Y/L=T(K/L)^\alpha
                $$
        \ee
\ee
\subsection{Forecase potential GDP based on growth accounting relations}
\be
    \item Growth Accounting Relations
        $$
        \Delta Y/Y=\Delta A/A+\alpha\times(\Delta K/K)+(1-\alpha)(\Delta L/L)
        $$
        i.e. growth rate in potential GDP = long-term growth of tech 
        + $\alpha$ long-term growth rate of capital
         + (1-$\alpha$)*(long-term growth rate of labor)
        \\ The growth of technology is not observable. Can be estimated from previous
        data: ex-growth rate - ex-growth rate from L and K
\ee
\subsection{Explain how natural resources affect economic growth and evaluate the arument
that limited availability of natural resources constrains economic growth}
\be
    \item Access to natural resouces does not require ownership of resources.
    \item Another theory: ownership of natural resources may actually inhibit growth. 
        \ra Dutch disease: global demand for natural resouces  drives up the coutries
        currency, making all other exports more expensive and uncompetitive.
\ee
\subsection{Explain how demographics, immigration, and labor force participation
affect the rate and sustainability of economic growth}
\be
    \item Labor Supply Factors
        \be
            \item Demographics: A countries age distribution. Countries with younger
                age will have a higher potential growth.
            \item Labor force participation.
            \item Immigration: a potential source in developed countries \Ra increase work force
            \item Average hours worked
        \ee
\ee
\subsection{Explain how investment in physical capital, human capital, and technological
development affects economic growth}
\be
    \item Human capital: knowledge and skills that individuals possess. Can be enhanced
        via education.
    \item Physical capital: infrastructure, computers, telecommunications(ICT)
        AND non-ICT capital(machineary, transportation and non-residential construction).
        More investment in physical capital \Ra Good GDP growth.
        \\ MOre investment may enhance the tech improvements.
    \item Technological development. Investment in tech will increase the productivity.
    \item Public infrastructure: like roads, bridges, and municipal facilities. 
        This will enhance total productivity. Because the private investment will not
        invest these public things for their little returns.
\ee
\subsection{Compare classical growth theory, neoclassical growth theory, and endogenous
growth theory}
\be
    \item Classical growth theory: In the long-term, population growth increases whenever
        there are increases in per capita income above subsistence level due to increase
        in capital or tech progress. \Ra Growth in real GDP per capita
        is not permanant. \Ra This is not supported by observed facts.
    \item Neoclassical Growth theory:
        \be
            \item Estimate steady state growth rate. Equilibrium economy is when the output-to-capital
                ratio is constant. When the output-capital ratio is constant, the labor-to-capital
                ratio and output per capita also grow at the equilibrium rate. Check textbooks here.
            \item Based on Cobb-Douglas function, 
                \be
                    \item Sustainable growth of output per capita: $g^\ast=\frac{\theta}{1-\alpha}$,
                        where $\theta$ is the growth rate in techonology, and $1-\alpha$ 
                        is the labor's share of GDP.
                    \item Sustainable growth rate: $G^\ast=\frac{\theta}{1-\alpha}
                        +\Delta_L$, which is the growth rate of output per  capita plus
                        the growth of labor.
                    \item Comments
                        \be
                            \item Caital deepening will not affet the growth rate in the long run.
                        \ee
                \ee
        \ee
    \item Endogenous Growth Theory
        \be
            \item Technological growth is a result of investment in physical and human capital. Returns to capital are constant.
            \item Private investments in R\&D also benefits all economy.
        \ee
\ee
\subsection{Explain and evaluate convergence hypoteses}
\be
    \item Absolute convergence: Less developed countries will achieve equal living standards
        overtime.
    \item Conditional convergence: Convergence in living standards will only occur for countries with the same savings rates, population
        growth rates and production functions. 
    \item Club convergence: Countries may be part of a club. Poorer countries that are part of the club will catch up
        their richer peers. Institutional changes can help a country to join the club. 
        Those are not in the club will never catch up.
\ee
\subsection{Describe the economic rationale for governments to provide 
incentives to private investments in technology and knowledge.}
R\&D are risky. Governments support may provide incentives to private R\&D, and therefore
boosts the growth of the overall economy.
\subsection{Describe the expected impact of removing trade barriers on capital investment 
and profits, employment and wages, and growth in the economies involved.}
\be
    \item Increased investment from foreign savins
    \item Allows focus on industries where the country has advantage.
    \item Increased markets
    \item Increased sharing of tech
    \item Increased competition removes bad firms and rellocating assets.
\ee

\section{Reading 15:Economics of Regulation}
\subsection{Describe classifications of regulations and regulators}
\be
    \item Regulations: i. Statues; ii. Administrative regulatinos; iii. judicial law
    \item Regulators: government agencies/indepedent regulators/outside bodies. Independent regulators
        including self-regulating organizations that regulates and represents their members.
        Outside bodies will not regulate, but their products are referenced by regulators.
\ee
\subsection{Describe uses of self-regulation in financial markets}
\be
    \item US: FINRA is an SRO recognized by SEC.
    \item In civil-law countries, independent SROs are rare, and government agencies
        fulfill the role of SROs.
    \item In common=law countries, independent SROs are historically good.
\ee
\subsection{Describe the economic rationale for regulatory intervention}
\be
    \item Economic Rationale for Regulation. Regulations are needed when
        \be 
            \item Information frictions. When information is not equally availabel or distributed.
            \item Externalities. 
        \ee
\ee
\subsection{Describe regulatory interdependencies and their effects.}
\be
    \item Regulatory Interdependencies.
        \be
            \item Regulatory capture theory: Regulators will at some point in time
                be influenced or controlled byt the industiry that is being regulated.
                Because the regulators will be influenced by the industry, and the
                experience will sometimes lead to impartial conclusions.
            \item Regulatory competition: Regulatory difference betweeen jurisdictions will lead to it.
                Regulators compete to provide the most business-friendly environment.
            \item Regulatory arbitrage: businesses find a coutry that best for itself.
        \ee
\ee
\subsection{Describe the tools of regulatory intervention in markets}
\be
    \item Price mechanisms
    \item Restricting/requiring certain activities. Ban certain activities or 
        require to perform some activities.
    \item Provision of public goods or financing private projects. 
\ee
\subsection{Explain purposes in regulating commerce and financial markets}
\be
    \item  Regulating commerce: Government regulations, including company laws, tax laws,
        contract laws, competition laws, banking laws, bankruptcy laws and dispute resolution systems.
        \\This laws may help or hinder commerce.
    \item REgulating financial markets: regulation of securities markets and regulation of 
                financial institutions. -- protecting investors, creating confidence in
                the markets, and enhancing capital formation.
        \be
            \item Regulation of security markets
            \item Regulation of Financial Institutions: Prudential supervision,
                the monitoring and regulation of financial institutions to reduce
                system-wide risks and to protect investors. Cost-benefit analysis should include
                hidden costs.
        \ee
\ee
\subsection{Describe anticompetitive behaviors targeted by antitrust laws globally and evaluate
the antitrust risk associated with a given business strategy.}
Antitrust regulation works to promote domestic competition. Like blocking a merger that leads to
excessive concentration of market share. International companies may be subject to antitrust
laws in different countries.
\subsection{Benefits and costs of regulation}
Costs include the implementation cost and the cost of the regulation to the private
sector.
{\it Regulatory burden}: the cost of compliance for the regulated entity. 
Regulatory burden - benefits that private sector receives = Net regulotry burden.
\subsection{Evaluate how a specific regulation affects and industry companly, or security}
\be
    \item Can help or hinder the industry or the company.
    \item Not necessarily always costly for those that being regulated.
    \item May introduce inefficiencies in the market. For example, government bailout of financial
        institutions may convey a message that companies will be helped. And the credit
        spreads will not fully reflect their risk.
    \item Certain industries have more exposure to certain types of regulations.
\ee


\section{Reading 16: Intercorporate Investments}
\subsection{Describe the classification, measurement, and disclosure under IFRS for
1) Investments in financial assets, 2) Investments in associates, 3) joint ventures, 4)
bussiness combinations, and 5) special purpose and variable interest entities}
\subsection{Distinguish between IFRS and US GAAP in the classification, measurement, and disclosure
of things above.}
\be
    \item Classification: a. Investments in financial assests. b. Investments in associates (investing
        firm has a significant influence but not control). c. Bussiness combinations.
        \be
            \item Financial assets. Ownership $<$ 20\%. Accouting treatment:
                \be
                    \item IFRS: held-to-matruity, available-for-sale, fair value through profit/loss.
                    \item GAAP: similar to IFRS.
                    \item IFRS 9 start from 1/1/2018. Early adoption is allowed.
                \ee
            \item Investments in associates. Ownership 20\%$\sim$50\%. Most important thing is ``significant
                influence.'' Equity method is used.
            \item Bussiness combinations. Ownership $>$ 50\%. ``Controling" is important. The acquision method is used.
            \item Joint ventures. Equity method for it.
        \ee
    \item Reporting of Intercorporate investments
        \be
            \item Financial assets. Acquisition is recorded at cost, and dividend or interest income
                is in Income Statement.
                \be
                    \item Held-to-maturity. Debt securities that cannot be sold prior to maturity
                        excepte in unusual circumstances. Long-term: reported on the balance sheet at the
                        amortized cost. Interest income(coupon cash flow adjusted for amortization
                        ) in the income statement but subsequent changes in fair value are ignored.
                    \item Fair value through profit or loss.
                        \\a. Held-for-trading: Debt/equity for the purpose of profiting in the near term. $<$ 3 month
                        Changes in fair value(realized or not) and dividend/interest are in Income State.
                        \\b. Designated at fair value: Report debt/equity that may be treated as held-to-maturity
                        or available-for-sale at fair value. Gains/Loss are in Income State.
                    \item Available-for-sale: are neither held-to-m nor held-for-trading. Reported on the balance at the
                        fair value. However, only the realized gains/losses and dividend or interest income are in the
                        income statement. Unrealized gains/losses are in comprehensive income. When sold, these unrealized
                        things will move to income statement.
                        \\NOTE: In IFRS, unrealized gains or losses on available-for-sale {\bf sale} 
                        that from foreign exchange movements are in the income
                        statement. In USGAAP, the entired unrealized gain/loss are recognized in equity.
                        \\ Available-for-sale {\bf Equity}, the treatments are similar in IFRS/USGAAP.
                \ee
        \item Reclassification of Investments in Fiancial Assets.
            \be
                \item IFRS: a.does not allow reclassiication into/out of the designated at fair value. b.Out of the held-for-trading
                    is severely restricted. \\c.Debt securities in available-for-sale can be reclassified as held-to-maturity. The value will be 
                    remeasured to reflect its fair value at the time it is reclassified. 
                    \\d. Held-to-maturity: can be reclassified as available-for-sale. Carrying value is remeasured
                    t the fair value, and any difference is recoreded in comprehensive income.
                \item USGAAP: 
                    \be
                        \item Permit reclassification into/out of held-for-trading or designated at fair value.
                            Unrealized gains on the income stmt is reclassified. 
                        \item Reclassificiation out of available-for-sale to held-for-trading, the cumulative g/l
                            in comprehensive income will be recognized in income.
                        \item Out-of-available for sale to held-to-maturity: G/L in comprehensive income stmt will
                            be amortized over the remaining life of the security.
                            \item Out of held-to-maturity to available-for-sale: Unrealized G/L goes into comprehensive income
                            stmt.
                        \item Summary\\
                            \begin{tabular}{ccc}
                            \hline
                            From & To & Unrealized G/L \\
                            \hline
                             Fair value w/ G/L*   & Any   &Income Statement\\
                             Held-to-maturity   & Fair value*  &  Income statement \\
                             Held-to-mat   & Available-for-sale   & Other comprehensive income\\
                             Available-for-sale & Held-to-maturity & Amortize out of other comprehensive income\\
                            Available-for-sale  & Fair value w/ G/L* & Transfer out of other comprehensive income\\
                            \hline
                            *: Restricted under IFRS
                            \end{tabular}
                    \ee
            \ee
        \item Impairment of Fianancial Assets: Held-to-Maturity(HTM) and available-for-sale (AFS) evaluabed for impairment
            at each reporting period.
            \be
                \item US GAAP. If its decline in value is determined to be other than temporary. HTM/AFS, the write-down
                to fair value is treated as a realized loss.
                \item US GAAP Reversals: NOT allowed.
                \item IFRS: Impairments are in the income stmt. Impairment of a debt or equity seurity
                $\Leftarrow$ at least one loss evet HAS occured, and its effect
                on the security's future cash flows can be estimated reliably.
                \\Debt: loss events -- default on payments
                \\Equities: loss evets -- fair value has experiened a decline, and
                it's unlikly to recover.
                \\HTM security: if it's impaired, its carrying value will be the 
                PV of future cash flows, using the interest rate when the security
                was PURCHASED.
                \item IFRS Reversals: Permited on HTM, available-for-sale. Not permitted
                    for equity.
            \ee
        \item Analysis of Investments in Financial Assets: Seperate a firm's operating
            results from its investment results. 
            \\For comparison: market values for financial assets.
            \\ Remove nonoperating assets when calculating the return on operating
            assets ratio.
            \\ Investment classification will be misleading.
        \item IFRS 9 (New standards)
            \be
                \item Instead of HTM, availabel-for-sale, and held-for-trading,
                    Using new terms: amortized cost, fair value through proft or loss
                    (FVPL), and fair value through other comprehensive income (FVOCI)
                \item Amortized cost (For debt securities only): If the securities are
                    \be
                        \item Business model test: being held to collect contractual cash
                            flows
                        \item Cash flow characteristic test: the contractual cash
                            flows are eithe principal or interest on principal only.
                    \ee
                \item Fair Value Through Profit or Loss (for debt and securities)
                    \be
                        \item Debt: can be FVTPL if held-for-trading, or Amortized cost
                            results in an accounting mismatch.
                        \item Equity: Must be FVTPL if it is held-for-trading. Other equity
                            can be FVTPL or fair value trhough OCI, but once classified, the choice
                            cannot be reversed.
                    \ee
                \item Fair Value Through OCI (Equity Only)
                    =Available-for-sal
            \ee
        \item Reclassification under IFRS 9
            \be
                \item Reclassification of Equity is not allowed.
                \item  Reclassification
                    of debt from amortized cost to FVPL or vice versa is OK only 
                    if the business model has changed. Unrecognized G/L on debt securities
                    carried at amortized cost and reclassified as FVPL are in the income stmt.
                \item Debt that out of FVPL: measured at amortized cost transfered at fair value
                    on the transfer date, and the fair value becom the carrying amount.
            \ee
        \item Investments in Associates
            \be
                \item Using equity method.
                \item Initial investment is recorded at cost and reported on balance
                    sheet as a noncurrent asset.
                \item Subsequent: proportional share of earnings increases 
                    the investment account on the balance
                    sheet, and is recognized in the income stmt. 
                    Dividends recevied are treated as a return of capital, and 
                    reduce the investment account, will no be in income stmt.
                \item If the investee has a loss, investor will have a proportionate loss
                    in balance, and income stmt.If the investment account on balance sht reduce to
                    0, we stop using equity method until the earnigs recovered.
            \ee
        \item Fair Value Option
            \be
                \item USGAAP allows equtiy method investment to be recored at fair value.
                \\ IFRS: the fair value only good to venture capital firms, mutal funds and similar firms.
                \\Decision to use FVO is irrevocable. If use FVO, any changes are in income stmt.
                \item Excess of Purchase Price Over Book Value Acquired. 
                    \be
                        \item At the acquisition date: the excess of the purchase
                            price over the proportionate share of book value is allocated
                            to the investee's identifiable assets and liabilities based on their fair
                            values, and in investor's balance sheet. The remainder is good will.
                        \item Investor need to recognize expense based on the excess amount assigned 
                            to the investee's asset and liabilities.
                        \item Investor may need to include additional depreciation
                            proportionate of the Excess of purchase price. See Notes-2 P11
                            examples and textbooks.
                    \ee
                \item Impairments of Investments in Associates:
                    \be
                        \item Equity method investments need tests for impairment.a
                        \item GAAP: Fair value of the investment < the carrying value(investment account on 
                            the balance sheet), and decline is permanent. Write-down to fair value,
                            loss in income stmt.
                        \item IFRS/GAAP: asset cannot write up
                    \ee
                \item Transactions with the Investee
                    Profit from these transactions deferred until the profit is
                    confirmed through use/sale to a third party.
                    \be
                        \item Upstream(investee to investor): investee recognized
                            all profit in its income stmt. Eliminate its proportionate
                            share of the profit.
                        \item Downstream(investor to investee). Investor recognize
                            profit in its income stmt. Eliminate the proportionate share
                            of unconfirmed profit.
                    \ee
                \item Analytical Issues for Investments in Associates.
                    \be
                        \item Equity method may have higher earnigs.
                        \item Investor only report investee's proportionate share of equity.
                            Investee's debt are ignored, and leverage is lower.
                        \item Proportionate shaore of Investee's earnings may be reinvested, not
                            available to investor via dividend.
                    \ee
            \ee
        \item Bussiness Combinations
            \be
                \item Classification:
                    Acquisition method is required for business combinations.
                    \be
                        \item IFRS: None
                        \item GAAP:
                                \\-Merger. Acquiring firm survived.
                                \\-Acquisition. Acqing and Acqed continue to exist in 
                                    a parent-subsidiary form. Not 100\% of sub is owned by parent.
                                \\- Consolidation. A new entity absorbs both of companies.
                    \ee
                \item Accounting methods
                    \be
                        \item Purchase method
                        \item Pooling-of-interests method (eliminated)=
                            uniting-of-interests method in IFRS
                            \\- Just combine assets and liabilities.
                            \\- Two companies combined using historical book vales
                            \\- Operating results are restated, as two have been always combined.
                            \\- Ownership interests continue, and former accounting bases maintained.
                        \item Acquisition method
                            \\- A, L, Revenue, Expense of sub are combined with the parent. Intercompany
                            transactions are excluded. Stock holder's equity is ignored. Because this
                            is not controlled by the company.
                            \\- noncontronling interest account may be needed for proportionate asset that
                            are not owned by the parent. Check examples.
                        \item Good will in acquisition    
                            \\- Goodwill. Fair value for identifiable assets/liabilities.
                            Any remainder will be unidentifiable A/L \Ra Goodwill
                            \\--GAAP: full goodwill. Fair value of the sub(calculated by acquired ratio) - Fair value 
                            of net identifiable net assets of the subsidiary; IFRS can use full goodwill
                            or partial goodwill, partical goodwill = purchase price - (\%owned*FV of net identifiable
                            asset)
                            \\Noncontrolling interest: For Full good will - nci based on the 
                            acquired company's fair value. For Partial goodwill -
                            nci based on the fair value of the acquired company's identifiable net
                            assets.
                        \item Annual test impariment of Goodwill
                            \\ IFRS: carrying amount of cast generting unit $>$ the recoverable amount
                            \\ GAAP: 2 steps. Carrying value of the reporting unit $>$ the fair value; 
                            the loss = carrying value of the good will $-$ the implied fair value of the goodwill.
                    \ee
            \ee
        \item Bargain Purchase: If acquisition price $<$ fair value of net asset aquired, gain should be in income stmt for 
            GAAP and IFSR.
        \item Joint Ventures: 
            \be
                \item One entitiy shared by multiple investors. Equity method in GAAP and IFRS.
                \item Rare case: Proportionate consolidation method is OK for GAAP/IFRS. 
                    In Proportionate consolidation, investor only reports the proportionate
                    share of assets, l, reve, expense. No minority owner's interest.
            \ee
        \item Special Purpose and Variable Interest Entities
            \be
                \item SPE: Special purpose entity. Isolate certain A and L of the sponsor.
                    SPE is often off-balanced-sheet. Thus enhance the ratios.
                \item VIE is a special SPE in FASB. Consolidated by the primary beneficiary.
                    VIE Characteristics:
                    \be
                        \item At-risk equity, insufficient to finance the entity's activities without additional support.
                        \item Equity investors lack: decision making rights, obligation to absorb loss, or the right
                            to recevie expected returns.
                    \ee
                \item IFRS: Sponsoring entity must consolidate if it controls SPE.
            \ee
    \ee
    \item Analyze how different methods used to account for intercorportate
        investments affect financial statements and ratios.
        \\ Four important effects, Equity/Proportionate consolidation/Acquisition
        \be
            \item All 3 report the same Net Income.
            \item Equity: Equity method = Proportionate = Acquisition method - minority interest
            \item Assets and Liabilities: Acquision $>$ Proportionate consolidation $>$Equity 
            \item Revenues and expenses: Acquision $>$ Proportinate consolidation $>$ Equity
        \ee
\ee


\section{Reading 17: Employee Compensation: Post-Employment and Share-Based}
\subsection{Descreibe the types of post-employment benefit plans and implications for financial reports}
Types: Defined-contribution plan and Defined-benefit plan. For defined-contribution plan, accounting is easy. Just
the employer's contribution.\\
Defined-benefit:
\be
    \item Usually via a separate legal entity, like a trust.
    \item funded status: difference between the pension obligation and the plan assets.
    \item Other post-employment benefits: basically healthcare benefits.
\ee
\subsection{Explain and calculate measures of a defined benefit pension obligation, i.e., 
PV of the defined benefit obligation and projcted benefit obligation, and net pension liability.}
\be
    \item Things to know
        \\-Projected Benefit Obligation, or Present Value of Defined Benefit Obligation under IFRS.
        :The PV of all future obligation, based on expected future salary increases.
        PVB will change from one period to the next.
        \be
            \item Current service cost: PV of benefits earned by during the current period.
            \item Interest cost: Increases in the obligation due to the passage of time.
                Interest will accrue. The cost = the pension obilgation at the beginning of
                the period times the discount rate.
            \item Past service costs: retroactive benefits awarded to employees when plan's changed.
                IFRS: expensed immediatedly. GAAP: ammortized over the average service life of 
                employees.
            \item Changes in actuarial assumptions: Gains/losses due to changes like mortality, 
                employee turnover, retirement age, and the discount rate.
            \item Benefits paid.
        \ee
    \item Balance Sheet Effects:
        \\Funded status = fair value of plan assets - PBO
        \\ Balance sheet asset(liability) = funded status. This is good for IFRS/GAAP.
\ee
\subsection{Describe the components of a company's defined benefit pension costs.}
\be
    \item Total periodic pension cost = employer contributions - (ending funded status - beginning funded status)
        \\TPPC = current service cost + interest cost - actual return on plan assets +/- actuarial losses,gains due
        to changes in assumptions affecting PBO + prior service cost.
    \item Periodic Pension Cost Reported in P\&L, i.e. Income stmt
        \be
            \item {\bf Current service cost}. Immediately recognized in income stmt.
                CSC is the increase in PBO since the employee worke one more period.
            \item {\bf Interest cost}. Immediately recognized. Increase in PBO due to the passage of time.
            \item {\bf Expected return on plan assets}. The return on the plan assets has no effect on the PBO.
                Use expected return to compute the reported pension expense. Difference
                in expected return and actual return are in "actual gains and losses"
                IFRS: expected rate of return is assumed = the discount rate to compute
                PBO.
            \item {\bf Actuarial gains and losses} Recognized in Other Comprehensive Income.
                has 2 components. G/L due to changes
                in actuarial assumptions; difference in actual/expected return. 
                IFRS: not amortized. GAAP: amortized with corridor.
            \item {\bf Corridor Approach.} If G/L$>$10\% of max(begining PBO, plan assets),
                the excess amount should be amortized over the remaining service 
                life of employees. Time can be shorter if wanted, but consistent.
            \item {\bf Past(prior) service costs.} If pension plan is changed, the change
                reported in OCI. And amortized of the remainig life of affected employees. 
                In IFRS: changes are reported in income stmt instantly.
            \item Summary\\
                \begin{tabular}{ccc}
                        \hline
                        Component & GAAP & IFRS \\
                        \hline
                        Current service costs & Income stmt & Income stmt \\
                        Past service costs  & OCI, amortized over life & Income\\
                        Interest costs & Income & Income \\
                        Expected return & Income & Income \\
                        Actuarial G/L & Amortized part in Income, Others in OCI & OCI\\
                        \hline
                \end{tabular}
            \item {\bf Presentation.} GAAP: income stmt aggreated and presented in one line.
                IFRS: components may be presented separately. 
            \item {\bf Capitalizing Pension Costs.} 
       \ee
\ee
\subsection{Explain and calculate the effect of a defined benefit plan's assumptions on the 
defined benefit obligation and periodic pension cost.}
3 Assumptions need disclosures.
\be
    \item {\bf Discount rate:} Interest rate to compute the PV of BO and the current service cost.
    \item {\bf Rate of compensation growth:} average annual increase rate of
        employee's compensation.
    \item {\bf Expected return on plan assets:} long-term rate of return on the plan's investments.
        Only good in GAAP, b/c in IFRS, it's equal to the discount rate.
\ee

To improve reports, a company
\be
    \item Increase the discount rate to reduce PBO, pension costs, and interest cost.
    \item Decrease the compensation growth rate to reduce futher benefit payments, PBO, and
        current service cost and interest cost.
    \item Increase the expected return on plan assets.
\ee
Ultimate healthcare trend rate: constant rate of a health care inflation.
\subsection{Explain and calculate how adjusting for items of pension and other
post-employment benefits affect financial stmts and ratios.}
One need to pay attention to different assumptions when compare companies:
\be
    \item Gross vs. net pension assets/liabilities. ROA will be lower with gross
        pension A/L; leverage ratios will be higher.
    \item Differnces in assumptions used: like discount rates.
    \item IFRS, GAAP. 
    \item Difference due to classification in the income stmt. GAAP: the entire 
        periodic pension cost in P\&L, including interest are operating expense.
        IFRS: can be in various line items.
\ee
\subsection{Interpret pension plan note disclosures including cash flow related 
information.}
If the difference between cash flow and total periodic pension cost is material,
the difference can be reclassified from Operating activities to Financing activities.
\subsection{Explain issues associated with accounting for share-based compensation}
\be
    \item Forms: stock options and outright share grants.
    \item Recording: issues for stocks -- the value needs estimatings. 
    \item SHould be spread over the period for which they reward the employee.
\ee
\subsection{Explain how accounting for stock grants and stock options affects
financial stmts, and the importance of companies assumptions in valuing these grants
and options.}
IFRS and GAAP are similar.
\be
    \item {\bf Stock options.} Expense is based on the fair value of options. Spread over 
        the service time(grant date to the actual date that employees can act). Net income
        and retaining earnings will decrease, but total-equity will not change.
    \item {\bf Determining Fair Value.} If on-market, use market price.
        Otherwise, Using different models to find it.
    \item {\bf Stock grants.} Compensation expense is based on the fair value of
        the grant date. Allocated over the service period.
    \item {\bf Stock appreciation rights.} It's different from stock options. 
        It gives the employee the right to receive compensation based on the increase in the price
        of the firm's stock over some threshold. No shares are issued. No dillustion, but 
        the company needs to pay cash.
    \item {\bf Phantom stock.} Similar to stock appreciation rights. But is based on the 
        performance of hypothetical stock
\ee


\section{Reading 18: Multinational Operations}
\subsection{Distinguish among presentation currency, functional currency and local currency.}
\be
    \item Definition:
        \\-Local currency: currency of the country being referred to.
        \\-Functional currency: determined by the management. The main currency the company uses.
        \\-Presentation (reporting) currency: The currency the parent company prepares stmts
\ee
\subsection{Describe foreign currency transaction exposure, including accounting for and 
disclosures about foreign currency transaction gains and losses}
\be
    \item Foreign currency denominated transactions are measured in the presentation
        currency at the spot rate on the transaction date. Currency risk arises when the
        transaction date and payment date differ, leads to differnt spot rate.
    \item If balance sheet date occurs before the transaction is settled, recognize G/L in
        blance sheet, and unrealized G/L in income stmt. When the transaction settled,
        additional G/L may need to be recognized.
    \item Analyst Issues: G/L due to currency in income stmt may be in operating or non-operating
        income. B/c accounting std do not provide any guides. Pay attention to this.
\ee
\subsection{Analyze how changes in exchange rates affect the translated sales of the subsidiary
and parent company}
\subsection{Compare the current rate method and the temporal method, evaluate how each
affects the parent company's balance sheet and income stmt, and determine which method is 
appropriate in variuos scenarios.}
\be
    \item Methods to translante financial stmts of sub to parent reporting currency
        \\- Remeasurement: converting the local to functional currency with temporal method.
        \\- Translantion: convert functional currency to paraent's reporting currency
        using the currenty rate method.
        \\- Define appropriate translation method. See P64 in notes, new version.
        \\- More definitions. a) Current rate: the exchange rate on the balance sheet rate.
        b) Average rate: the average exchange rate over the reporting period. c). historical rate:
        the actual when the transactions occurs.
    \item Apply the current rate method process:
        \be
            \item All income stms are translate at the average rate.
            \item All balance sheet accounts are translated at the current rate 
                {\it except for common stock, at historical rate}.
            \item Dividends are at the rate that applied when they were declared.
            \item Translation G/L is reported in shareholder's equity as a part
                of the cumulative translation adjustment.
        \ee
    \item Applying the Temporal Method
        \be
            \item Monetary A/L(fixed in the amount of currency) remeasured using the current exchange rate.
            \item All other A/L are nonmonetary assets,  like inventory, fixed assets,
                intangible assets.for example, Unearned(deferred) revenue. They are 
                remeasured in hisotyrical rate. ({\it Exception: non-money A/L on the balance sheet
                at fair value are remeasured at the current rate}).
            \item Common stock, dividends paid are at historical rate.
            \item Expense related to nonmonetariy assets are remeasured based on the 
                historical rates at the time of purchase.
            \item Revenues and all other expenses are at the average rate.
            \item Remeasurement G/L is in income stmt. 
        \ee
    \item Inventory and COGS under the Temporal Method.
       \\ Numerous historical exchange rate needs to be remembered. Inventory
                are complicated. Inventory and COGS are remeasured at different rates in 
                FIFO/LIFO.
    \item Parents Company Exposure to Changing Exchange Rates
        \be
            \item In Current rate method: Exposure in the net asset position of the subsidiary.
            \item In Temporal method: net monetary A/L are exposed.
        \ee
    \item Calculating the Translation/Remeasurement G/L
        \\G/L is reported in CTA, and GTP  is used to make A=L+E.
\ee
\subsection{Calculate the translation effects and evaluate the translation of a 
subsidiary's balance sheet and income }
\be
    \item -CR method: start with income stmt. As the net income here will be used 
        for the retained earnings in balance stmt.
        \\-Temporal method: start with blance stmt.
    \item Different results from CR and Temporal methods. Why?
        \be
            \item Income before translation G/L is different, due to the different 
                rate used for items. Example: COGS and depreciation, avearge rate
                in CR method and historical rate in Temporal.
            \item Translation G/L are different. Since net assets' are exposed to
                the depreciation of Local Currenty in CR, but net MONETARY assets
                are in temporal method.
            \item Net income is different. This is due to different exchange rate. Besides,
                in CR method, translation G/L are in CTA. In Temporal, remeasurement G/L are
                in income stmt.
            \item Total assets are different b/c inventory and net fixed assets are different.
        \ee
    \item
\ee
\subsection{Analyze how the current rate method and the temporal method affect financial 
statements and ratios.}
\be
    \item Pure Balance Sheet and pure Income Stmt ratios. PURE balance sheet and pure
        income statement ratios 
    \item Mixed Balance Sheet/Income Statement ratios. CR result in small changes.
        \\ Key points to remember
        \\ --Pure balance sheet/pure income ratios will be the same.
        \\ --If foreign currency is depreciating, translated mixed ratios (with
        income stmt in up and end-of-period balance sheet item down) will be larger.
    \item Compare ratios from Temporal method and current rate method. Compare the rates
        is the key.
        \be
            \item Determine whether the foreigen currency is appreciating/depre.
            \item which rates is on numberator or denominator.
        \ee
\ee
\subsection{Analyze how alternative translation methods for subsidiaries operating
in hyperinflationary economies affect financial stmts\& ratios}
\be
    \item
\ee
\end{document}


